Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-03-24 DGMM2025/paper.tex
latex algorithm

\usepackage{changes}
%\usepackage{amstex}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

@@

>>>>

\usepackage{changes}
\usepackage{amstex}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    Definition Zd
    Definition Cell complex
    Definition Star

@@

    \begin{algorithm}
        \caption{Given a cell complex C and a radius \(r\), compute the visibility at every point of C up to distance \(r\).}
        \label{alg:visibility}
        \begin{algorithmic}

            \Function{CheckI}{$I$: Interval, ComplexI: list of Interval}
                \State $[a, b] \gets I$
                \State $Result \gets \emptyset$
                \For{each interval $J$ in ComplexI}
                    \State $[c, d] \gets J$
                    \If{$\text{Size}(I) \leq \text{Size}(J)$}
                        \State $Result \gets Result \cup [c-a,d-b+1]$
                    \EndIf
                \EndFor
                \State \Return Result
            \EndFunction

            \Function{MatchVector}{\text{CurrentIResult}: list of Interval, VectorI: list of Interval, ComplexI: list of Interval}
                \For{each interval $I$ in VectorI}
                    \State $\text{CurrentIResult} \gets \text{CurrentIResult} \cap \Call{CheckI}{I, \text{ComplexI}}$
                \EndFor
                \State \Return \text{CurrentIResult}
            \EndFunction

            \Function{Visibility}{\text{C}: Cell complex, \text{Radius}: integer}
                \State $FigLattices \gets \Call{GetStarFigLattices}{C}$
                \State $Vectors \gets \Call{GetAllPrimalVectors}{Radius}$
                \State $Visibility: \text{list of boolean} \gets \emptyset$
                \State $minFInterval, maxFInterval \gets \Call{GetMinMaxInterval}{FigLattices}$
                \For{each $V$ in $Vectors$}
                    \State $VLattice \gets \Call{GetLattice}{\text{V}}$
                    \For{every shift $tx, ty$ in $FigLattices$}
                        \State $CurrentIResult \gets [minFInterval, maxFInterval]$
                        \State $StartingPoint \gets \Call{GetStartingPoint}{tx, ty}$
                        \For{each $Lattice$ in $VStarLattice$}
                            \State \begin{varwidth}[t]{\linewidth}
                                       $CurrentIResult~\gets~MatchVector(CurrentIResult,$\par
                                       \hskip\algorithmicindent $Lattice.intervals,$\par
                                       \hskip\algorithmicindent $\text{FigLattices}[StartingPoint + Lattice.position])$
                            \end{varwidth}
                        \EndFor
                        \State \Call{UpdateVisibility}{$Visibility$, $CurrentIResult$}
                    \EndFor
                \EndFor
                \State \Return $Visibility$
            \EndFunction

        \end{algorithmic}
    \end{algorithm}
